\documentclass[10pt, a4paper]{article}
\title{\textbf{Tim King-Kehl}}
\usepackage{courier}
\usepackage[margin=.5in]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    }
\urlstyle{same}
\date{}

\renewcommand{\abstractname}{} % Remove the word 'abstract' from abstract.

\begin{document}
\begin{center}
    \textbf{\Huge \scshape Tim King-Kehl} \\ \vspace{1pt}
    Papillion, NE \\ \vspace{1pt}
     402-575-0627 \ $|$ \ tkingkehl@gmail.com \\ \vspace{1pt} 
     \url{https://www.linkedin.com/in/tkingkehl/} \ $|$ \ \url{https://github.com/tkingkehl} \\ \vspace{1pt} 
\end{center}
\begin{abstract}
Site Reliability Engineer - Linux Administrator - Automation Enthusiast - Troubleshooter Extraordinaire
\end{abstract}

\section*{Work Experience}
\begin{itemize}
    \item \textbf{Senior Project Engineer} Union Pacific
    \begin{itemize}
        \item Manage 12,000+ Linux servers across multiple data centers. 3 RHEL-based OS varieties, 10+ OS versions. Perform day-to-day sys admin duties: troubleshooting, disk slicing, vendor POCs, server upgrades/migrations, and much more.
        \item Primary support/architect for GlusterFS, a clustered filesystem software. Completed upgrade from server/client version 4 to 6, across 700 total servers, with 100\% uptime.
        \item Primary support/architect for Linux patching, including: uploading custom packages to Spacewalk repositories, pulling down upstream packages into our in-house RPM repository, cutting the repositories and patching on a quarterly basis, and working with application teams to ensure reboots are performed.
        \item Primary support/architect for Rundeck automation suite, including Ansible playbooks and more, used for Linux server build automation, and other automation tasks.
        \item Primary support/architect for Prometheus server metric monitoring platform, integrated with Grafana.
        \item Assist with Linux architecture plans for UP's Azure journey.
        \item Write various Chef cookbooks, Bash scripts, and more ad-hoc/break-fix scripts for automation purposes.
        \item Mentor and assist colleagues and juniors from my team and others across the Tech org.
    \end{itemize}
    \item \textbf{Project Engineer} Union Pacific
    \begin{itemize}
        \item Managed the Distributed (Unix/Linux, Windows) and Mainframe (TSO, CA7) production environments.
        \item Actively monitored alert systems and responded to application and infrastructure related alarms.
        \item Oversaw and deployed production application changes.
        \item Performed call leader duties during critical system outage situations, escalated to proper support teams, and ensured swift resolution.
        \item Developed and maintained scripts and programs to assist with the automation of daily work.
        \item Lead disaster recovery training exercises, performed failovers of critical systems and applications between multiple data center locations.
    \end{itemize}
    \item \textbf{IT Intern} Union Pacific
    \begin{itemize}
        \item Provided Tier 1 Phone support and analysis.
        \item Quickly troubleshot problems and found solutions by using available resources.
        \item Assisted in training of new full time and interning analysts.
    \end{itemize}
\end{itemize}
\section*{Education}
    \begin{minipage}{0.5\textwidth} % Adjust the width as needed
        \raggedright % Align text to the left
        Bachelors of Science in Computer Science
      \end{minipage}
      \begin{minipage}{0.5\textwidth} % Adjust the width as needed
        \raggedleft % Align text to the right
        2014 \-- 2019
      \end{minipage}
      \begin{itemize}
      \item University of Nebraska, Omaha
    \end{itemize}

\section*{Skills}
Linux - Bash - Ansible - Data Center - Troubleshooting - Rundeck - Python - Pacemaker - CentOS - Oracle - Automation - Chef - GlusterFS - Patching - Unix - Azure - Server Administration - Terraform - Powershell - Documentation

\end{document}